Introduction

### 2025-12-03 Intro.Rmd
Add descriptions for visualization figures

@@

@@

@@

@@

@@

@@

What does this mean? ^

>>>>

**Description:** A simple bar chart showing the imbalance between clients who subscribed to a term deposit (“yes”) and those who did not (“no”), with the majority belonging to the “no” category.

@@

**Description:** A stacked bar chart illustrating the proportion of subscription outcomes across different job types, with retired and student occupations showing relatively higher subscription rates.

@@

**Description:** A proportional bar chart comparing subscription rates across education levels, indicating that clients with tertiary education have a higher tendency to subscribe.

@@

**Description:** A stacked bar chart showing subscription proportions by marital status, revealing that single clients have a slightly higher subscription rate compared to married or divorced clients.

@@

**Description:** A proportional bar chart comparing subscription outcomes by contact method, with cellular contacts showing a notably higher subscription rate than telephone or unknown contact types.

@@

**Description:** A stacked bar chart depicting how the outcome of previous marketing campaigns influences current subscription rates, with previous “success” outcomes leading to higher subscription proportions.

@@

**Description:** A line plot with points showing how the subscription success rate declines as the number of contacts during the campaign increases, suggesting diminishing returns with repeated contact attempts.
